### 2021-09-01 sections/papers.tex
Update papers.tex

\item{\small Gonz\'alez-Bustamante, B., \& Garrido-Vergara, L. (2018). Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010. {\itshape Pol\'itica y Gobierno, XXV}(1), 31--64. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}
\end{benumerate}

@@

\begin{benumerate}{7}
\item{\small Olivares, A. {\itshape et al.} (2020). New Challenges, Approaches, and Perspectives in the Study of Political Elites. {\itshape Iberoamericana, XX}(74), 229--259. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}. \\{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}

@@

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2015). Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014. {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
\end{benumerate}

@@

\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G. (2012). Digital Campaigns: Branding or Political Participation? {\itshape M\'as Poder Local,} 12, 32--39. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
\end{benumerate}

>>>>

\item{\small Gonz\'alez-Bustamante, B., \& Garrido-Vergara, L. (2018). Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010. {\itshape Pol\'itica y Gobierno, XXV}(1), 31--64. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}

\end{benumerate}

@@

\begin{benumerate}{8}

\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B. (2020). Senior Public Managers: A Novel Dataset on Members of the Chilean Civil Service. {\itshape Revista de Gestión Pública, IX}(2), 151--169. {\footnotesize \scshape [in Spanish and English]}. {\scshape doi}: \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}}\vspace{1mm}

\item{\small Olivares, A. {\itshape et al.} (2020). New Challenges, Approaches, and Perspectives in the Study of Political Elites. {\itshape Iberoamericana, XX}(74), 229--259. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}. \\{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}

@@

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2015). Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014. {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190. {\footnotesize \scshape [in Spanish]}. \\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}

\end{benumerate}

@@

\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G. (2012). Digital Campaigns: Branding or Political Participation? {\itshape M\'as Poder Local,} 12, 32--39. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}

\end{benumerate}
